\documentclass[11pt]{article}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{listings}

\begin{document}

% PDF version.
% \textit{PDF version available \href{/cv.pdf}{here}.}

\subsection{Contact}
\label{sec:contact}

% TODO: update formatting/etc.
\begin{tabularx}{\textwidth}{ll}
    & \href{mailto:ryan.rpwilliams@gmail.com}{ryan.rpwilliams@gmail.com} \\
    & \href{https://www.linkedin.com/in/ryan-paul-williams}{LinkedIn} \\
    & \href{https://github.com/williamsryan}{GitHub} \\
\end{tabularx}

\subsection{Education}
\label{sec:education}

\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{8cm}>{\raggedright\arraybackslash}r}
    \textbf{Northeastern University}, Boston, MA & (expected) Fall 2023 \\
    \textit{PhD Computer Science} & \\
    \textbf{University of Southern California}, Los Angeles, CA & Dec. 2014 \\
    \textit{MS Computer Science} & \\
    \textbf{University of California, Los Angeles}, Los Angeles, CA & Jun. 2012 \\
    \textit{BS Mathematics} & \\
    \textit{BA Design \& Media Arts} & \\
\end{tabularx}

\subsection{Publications}
\label{sec:publications}
\subsubsection{Conference Papers}
\textbf{Ryan Williams}, Anthony Gavazzi, Engin Kirda (2023).
\href{https://ieeexplore.ieee.org/abstract/document/10123487}{Solder: Retrofitting Legacy Code with Cross-Language Patches.}
SANER 2023.

Anthony Gavazzi, \textbf{Ryan Williams}, Engin Kirda, Long Lu, Andre King, Andy Davis, Tim Leek (2023).
\href{https://www.usenix.org/system/files/sec23summer_41-gavazzi-prepub.pdf}{A Study of Multi-Factor and Risk-Based Authentication Availability.}
USENIX Security 2023.

Tongwei Ren, \textbf{Ryan Williams}, Sirshendu Ganguly, Lorenzo De Carli, Long Lu (2022).
\href{https://link.springer.com/chapter/10.1007/978-3-031-25538-0_40}{Breaking Embedded Software Homogeneity with Protocol Mutations.}
LNICST 2022.

Amogh Pradeep, Hira Javaid, \textbf{Ryan Williams}, Antoine Rault, David Choffnes, Stevens Le Blond, Bryan Alexander Ford (2022).
\href{https://infoscience.epfl.ch/record/301155}{Moby: A blackout-resistant anonymity network for mobile devices.}
PETS 2022.

Mansour Ahmadi, Reza Mirzazade Farkhani, \textbf{Ryan Williams}, Long Lu (2021).
\href{https://www.usenix.org/system/files/sec21-ahmadi.pdf}{Finding Bugs Using Your Own Code: Detecting Functionally-similar yet Inconsistent Code.}
USENIX Security 2021.

Elin Carstensdottir, Erica Kleinman, \textbf{Ryan Williams}, Magy Seif Seif El-Nasr (2021).
\href{https://dl.acm.org/doi/abs/10.1145/3411764.3445540}{”Naked and on Fire”: Examining Player Agency Experiences in Narrative-Focused Gameplay.}
CHI 2021.

\subsubsection{Journal Papers}
\textbf{Ryan Williams}, Tongwei Ren, Lorenzo De Carli, Long Lu, Gillian Smith (2021).
\href{https://dl.acm.org/doi/full/10.1145/3487568}{Guided Feature Identification and Removal for Resource-constrained Firmware.}
TOSEM 2021.

\subsubsection{Workshop Papers}
Alexander Heinricher, \textbf{Ryan Williams}, Ava Klingbeil, Alex Jordan (2021).
\href{https://dl.acm.org/doi/abs/10.1145/3460946.3464320}{Weldr: fusing binaries for simplified analysis.}
SOAP 2021.

\subsection{Working Experience}
\label{sec:working-experience}
TODO

\subsection{Teaching Experience}
\label{sec:teaching-experience}
TODO

\subsection{Professional Services}
\label{sec:services}
TODO

\subsection{Technical Skills}
\label{sec:skills}
TODO

\end{document}
